### 2011-08-01 doc/theses/svirec/prace.tex
fixing abstract

Abstract:
Knowledge of integrity constraints covered in the XML data is an important aspect of efficient data processing. However, although the integrity constraints are defined for the given data, it is a common phenomenon that data violate the predefined set of constraints. Therefore detection of these inconsistencies and consecutive repair has emerged. This work extends and refines recent approaches to repairing XML documents violating defined set of integrity constraints, specifically so-called functional dependencies. The work propose the repair algorithm incorporating the weight model and also involve user into the process of detection and subsequent application of appropriate repair of inconsistent XML documents. Experimental results are part of the work.
% abstrakt v rozsahu 80-200 slov v angličtině; nejedná se vąak o překlad
% zadání diplomové práce

@@

%%% Seznam pouľité literatury
\nocite{*}
\bibliographystyle{ieeetr}
\bibliography{literatura}

>>>>

Abstract:
Knowledge of integrity constraints covered in XML data is an important aspect of efficient data processing. However, although integrity constraints are defined for the given data, it is a common phenomenon that data violate the predefined set of constraints. Therefore detection of these inconsistencies and consecutive repair has emerged. This work extends and refines recent approaches to repairing XML documents violating defined set of integrity constraints, specifically so-called functional dependencies. The work proposes the repair algorithm incorporating the weight model and also involve a user into the process of detection and subsequent application of appropriate repair of inconsistent XML documents. Experimental results are part of the work.
% abstrakt v rozsahu 80-200 slov v angličtině; nejedná se vąak o překlad
% zadání diplomové práce

@@

\clearpage
\phantomsection
\addcontentsline{toc}{chapter}{Bibliography}
%%% Seznam pouľité literatury
\nocite{*}
\bibliographystyle{ieeetr}
\bibliography{literatura}
